Evolution of pre-copulatory and post-copulatory strategies of inbreeding avoidance and associated polyandry

### 2017-09-20 pre_post.tex
Final tweaks before sending to JEB
Initial commit and fix first comment

\documentclass[12pt]{article}
\usepackage[top=1.25in, bottom=1in, left=1.25in, right=1in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{datetime}
\setkomafont{\rmfamily\bfseries\boldmath}
\usepackage{wrapfig,floatrow}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{mathabx}
\usepackage{color}
\usepackage{wasysym}
\usepackage{lipsum}
\floatstyle{plain}
\restylefloat{Fig.}

@@

From a female's perspective, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males following mating (i.e., post-copulatory inbreeding avoidance). Evolution of post-copulatory inbreeding avoidance is likely to be facilitated when females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}. Further, such polyandry might itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, potentially including males that were unavailable for initial mate choice \cite[e.g.,][]{Reid2015, Duthie}. Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm (i.e., under conditions of a `fair raffle').

@@

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.85]{figures/poly_costs.png}
\end{center}
\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely. Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry. Dotted lines demarcate mean allele values of zero.}
%\label{Fig1}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.60]{figures/Pp_vals.png}
\end{center}
\caption{Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with identical initial conditions, default parameter values, and zero costs. Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations. Positive and negative allele values contribute to polyandry and monandry, respectively. In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line). Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations. Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively. Arrows and numbers indicate mean phenotype values. Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values.}
%\label{Fig2}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=1.00]{figures/rel_costs.png}
\end{center}
\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve. Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. In all panels, polyandry is cost free.}
%\label{Fig3}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=1.00]{figures/fixed_adapt.png}
\end{center}
\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.}
%\label{Fig4}
\end{figure}

>>>>

\documentclass[12pt]{article}
\usepackage[top=1.25in, bottom=1in, left=1.25in, right=1in]{geometry}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{rotating}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{lineno}
\usepackage{datetime}
\setkomafont{\rmfamily\bfseries\boldmath}
\usepackage{wrapfig,floatrow}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{mathabx}
\usepackage{color}
\usepackage{wasysym}
\usepackage{lipsum}
\usepackage{soul}
\floatstyle{plain}
\restylefloat{Fig.}

@@

From a female's perspective, inbreeding avoidance might be achieved by avoiding mating with related males (i.e., pre-copulatory inbreeding avoidance), or by biasing fertilisation towards unrelated males following mating (i.e., post-copulatory inbreeding avoidance). Evolution of post-copulatory inbreeding avoidance \textcolor{red}{\st{is likely to be facilitated when}} \textcolor{blue}{requires that} females express some degree of polyandry, defined as mating with multiple males during a single reproductive bout \cite[but see][]{Dougherty2016}. Further, such polyandry might itself evolve because it allows females to mate with additional unrelated males following an initial mating with a relative, potentially including males that were unavailable for initial mate choice \cite[e.g.,][]{Reid2015, Duthie}. Polyandry can thereby facilitate pre-copulatory inbreeding avoidance even without any post-copulatory female choice or otherwise biased fertilisation among sperm (i.e., under conditions of a `fair raffle').

@@

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.85]{poly_costs.eps}
\end{center}
\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) from simulations where post-copulatory inbreeding strategy is (A, C, E, and G) fixed to zero (i.e., random fertilisation) or (B, D, F, and H) allowed to evolve freely. Costs of polyandry ($c_p$) increase across rows from zero (A and B) to 0.01 (G and H). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate inbreeding avoidance or tendency for monandry, and positive values indicate inbreeding preference or tendency for polyandry. Dotted lines demarcate mean allele values of zero.}
%\label{Fig1}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=0.60]{Pp_vals.eps}
\end{center}
\caption{Relationships between (A and C) polyandry allele values and (B and D) monandry and polyandry phenotypes for simulations with identical initial conditions, default parameter values, and zero costs. Red lines in (A) and (C) show mean polyandry allele values across all individuals in a single simulation over 40000 generations. Positive and negative allele values contribute to polyandry and monandry, respectively. In the final generation, mean allele value was below (A) or above (C) zero (demarcated by the dotted line). Nevertheless, due to the threshold nature of expression of the polygenic polyandry phenotype, polyandry and monandry are expressed in both populations. Histograms in (B) and (D) show females' tendency for polyandry phenotypes in the final generation; white and grey shading indicates monandrous and polyandrous females, respectively. Arrows and numbers indicate mean phenotype values. Because each trait includes 10 diploid loci with additive effects, phenotype values are ca 20 times allele values.}
%\label{Fig2}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=1.00]{rel_costs.eps}
\end{center}
\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black) when (A and B) costly pre-copulatory inbreeding strategy ($c_{M} = 0.02$) can evolve and post-copulatory inbreeding strategy is (A) fixed for random fertilisation or (B) can also evolve, and when (C and D) costly post-copulatory inbreeding strategy ($c_{F} = 0.02$) can evolve and pre-copulatory inbreeding strategy is (C) fixed for random mating or (D) can also evolve. Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry. In all panels, polyandry is cost free.}
%\label{Fig3}
\end{figure}

\clearpage
\begin{figure}
\begin{center}				
\includegraphics[scale=1.00]{fixed_adapt.eps}
\end{center}
\caption{Mean allele values underlying tendency for polyandry (red), pre-copulatory inbreeding strategy (blue), and post-copulatory inbreeding strategy (black), given (A and B) fixed polyandry and post-copulatory inbreeding avoidance and (C and D) fixed post-copulatory inbreeding avoidance where the evolving inbreeding strategy is cost-free (A, $c_{M} = 0$; C, $c_{F} = 0$) or costly (B, $c_{M}=0.02$; D, $c_{F}=0.02$). Mean allele values (solid lines) and associated standard errors (shading) are calculated across all individuals within a population over 40000 generations across 40 replicate populations. Negative mean allele values indicate strategies of inbreeding avoidance or tendency for monandry, and positive values indicate strategies of inbreeding preference or tendency for polyandry.}
%\label{Fig4}
\end{figure}
